---
title       : Coursersa Project Developing Data Products 
subtitle    : Free Space on disks Server
author      : Julio B-M
job         : TIC responsible
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## The problem and solution

* I'm responsible of many servers of a company. I'm fear about getting low space on disks.  
* In Sep-2011 I made a python script that checks every fex minutes free space on disks on each server of my lan and logs in a file once a day the result.   
* If a disk gets 1GB low, the script sends me a email.  

**Now I want to see the log-data I got along these years graphically**.



--- .class #id 

## The data


The log file has this structure
```{r} 
datalog <- read.csv("libre_en_disco_log.csv", dec=",",head=TRUE,sep="\t")
head(datalog)
```

--- .class #id

## The ShinyApp


* I made this shinyapp  

https://juliobm.shinyapps.io/shiny_freespace

* You can choose server and the the page shows you only the disks that has the server.

* You can select a range date to show the data too.

* In another tab you can see the log file in table format.

* You can see the code at this link

https://github.com/juliobm/slidify_freespace



--- .class #id

## A graph example

```{r echo=FALSE}
library(ggplot2)
datalog <- read.csv("libre_en_disco_log.csv", dec=",",head=TRUE,sep="\t")
datalog$FECHA <- as.Date(datalog$FECHA)
midata <- datalog[datalog$DISCO=="C$" & datalog$SERVIDOR=="INTRANET",]
   
p <- ggplot(midata, aes(x=FECHA, y=GB)) +
      theme_bw() +
      #geom_histogram(binwidth = bin, colour="white") +
      geom_line(colour="black", stat="identity") +
      geom_smooth( aes(group=1),method="gam") +
      labs(y ="GB") +
      labs(x ="Date") +
      labs(title = "Free Space on INTRANET disk C$ in 2014") +
      scale_fill_brewer() +
      scale_x_date()
print(p)
```
